---
title: "GPU benchmark with Google Cloud (Using Sparkles Spray)"
author: "Remi Marenco"
date: "11/6/2018"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
```

### Overview

The goal of this analysis is to help researcher to know the resources to use for their machine learning
analysis.
It contains:
- CPU analysis
- GPU analysis
- Time
- Different kind of data type (small, medium, large)

The raw data are living [here]( https://docs.google.com/spreadsheets/d/1ctvK6JM-jaFBDgN8oY4n1Nj86OpvlMoGVBsR-Sk0t90/edit?usp=sharing)


### Contents
**Runtime per data size**

**Cost in function of time, depending on GPU**

### Runtime per data size

```{r runtime_per_data_size, warning=FALSE}
# Read the file we got from the google spreadsheet
benchmark <- read.csv(file="~/Dev/test_sparkles/remi_cloud_benchmarking/Benchmarking MOA Prediction Cloud - Data_to_process.csv",
                      header=TRUE, na.strings = c("", "NA"),
                      colClasses = c("factor", "integer", "numeric", "factor", "numeric", "factor", "numeric", "numeric"))
# Remove NAs / empty rows
benchmark <- benchmark %>% na.omit()

# Consider n1-highcpu equivalent to standard
benchmark <- benchmark %>% mutate(machine_type=replace(machine_type, machine_type=='n1-highcpu-2', 'n1-standard-2')) %>% as.data.frame()
benchmark <- benchmark %>% mutate(machine_type=replace(machine_type, machine_type=='n1-highcpu-8', 'n1-standard-8')) %>% as.data.frame()

# Remove standard1 sine this machine has not enough memory (3.75)
benchmark <- benchmark[benchmark$machine_type != 'n1-standard-1',]

# Add a column to combine machine_type with gpu

bench_run_time_per_machine_type_agg <- aggregate(benchmark, by=list(benchmark$machine_type, benchmark$gpu, benchmark$data_type),
                                                 FUN=mean,
                                                 drop=TRUE)
# Clean names
drops <- c("machine_type", "gpu", "data_type")
bench_run_time_per_machine_type_agg <- bench_run_time_per_machine_type_agg[, !(names(bench_run_time_per_machine_type_agg) %in% drops)]

# Rename Groups
colnames(bench_run_time_per_machine_type_agg)[colnames(bench_run_time_per_machine_type_agg)=="Group.1"] <- "machine_type"
colnames(bench_run_time_per_machine_type_agg)[colnames(bench_run_time_per_machine_type_agg)=="Group.2"] <- "gpu"
colnames(bench_run_time_per_machine_type_agg)[colnames(bench_run_time_per_machine_type_agg)=="Group.3"] <- "data_type"


# TODO: facet grid CPU ~ data size, with bar plot
plot_time_data_per_machine <- ggplot(data=bench_run_time_per_machine_type_agg, aes(y=log2(program_run_time_s/60),
                                                         x=data_type,
                                                         shape=gpu,
                                                         color=machine_type,
                                                         size=1)) + scale_size(guide = 'none')
plot_time_data_per_machine <- plot_time_data_per_machine + geom_point() + labs(x = 'Data size') + labs(y = 'Program runtime (log2 minutes)')
plot(plot_time_data_per_machine)
```

### Cost in function of time, depending on GPU

```{r cost_function_time_gpu}
# Plot time vs cost
# TODO: Switch axis
# TODO: Make size bubbles per data_type

# TODO: Bar plots with gpu/cpu stacked between
time_vs_cost <- ggplot(benchmark,
                       aes(x=program_run_time_s/60,
                           y=price_regular,
                           color=gpu)) + geom_point() + geom_smooth(method=lm)

# Labels
time_vs_cost <- time_vs_cost + labs(x = 'Program runtime (minutes)') + labs(y = 'Regular price ($)')
plot(time_vs_cost)
```
